Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-31 fmics/paper.tex
minor tweak fig 4,5 captions
tweak wordings in a couple of sentences

\begin{figure}[t]
  \centering \scalebox{0.65}{ \includegraphics{srs-modified.eps}}
   \caption{The block diagram showing the implementation of SRS in BLETC.}
  \label{fig:srs}
\end{figure}

@@

\begin{figure}[t]
  \centering \scalebox{0.8}{ \includegraphics{multi-rs.eps}}
  \vspace{-0.1in}
   \caption{The block diagram showing the implementation of each slice.}
  \label{fig:slice}
\end{figure}

@@

The function $\mathsf{true\_sum}$ is easily defined in terms of $\mathsf{exact}$, that is $\mathsf{true\_sum}\;D\;n\;t = \mathsf{exact}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)\;t$.
Since $\mathsf{RS}$ is also similarly defined in terms of the $\mathsf{output}$, Theorem~\ref{output_eq_exact} establishes a relationship between the values of the $\mathsf{RS}$ and $\mathsf{true\_sum}$.

>>>>

\begin{figure}[t]
  \centering \scalebox{0.65}{ \includegraphics{srs-modified.eps}}
   \caption{Block diagram showing the implementation of SRS in a BLETC.}
  \label{fig:srs}
\end{figure}

@@

\begin{figure}[t]
  \centering \scalebox{0.8}{ \includegraphics{multi-rs.eps}}
  \vspace{-0.1in}
   \caption{Block diagram showing the implementation of each slice.}
  \label{fig:slice}
\end{figure}

@@

The function $\mathsf{true\_sum}$ is easily defined in terms of $\mathsf{exact}$, namely, $\mathsf{true\_sum}\;D\;n\;t = \mathsf{exact}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)\;t$.
Since $\mathsf{RS}$ is similarly defined in terms of the $\mathsf{output}$, Theorem~\ref{output_eq_exact} establishes a relationship between the values of $\mathsf{RS}$ and of $\mathsf{true\_sum}$.
